Resolving the measurement uncertainty paradox in ecological management

### 2018-11-22 manuscripts/manuscript.tex
fix a few refs
rebuild pdf

\leavevmode\hypertarget{ref-sarsop-pkg}{}%
Boettiger, C., J. Ooms, and M. Memarzadeh. 2018. Sarsop: Approximate
pomdp planning software.

@@

\leavevmode\hypertarget{ref-Dorner2009}{}%
Dorner, B., R. M. Peterman, and Z. Su. 2009. Evaluation of performance
of alternative management models of Pacific salmon (Oncorhynchus spp.)
in the presence of climatic change and outcome uncertainty using Monte
Carlo simulations. (R. Hilborn, ed.)Canadian Journal of Fisheries and
Aquatic Sciences 66:2199--2221.

@@

\leavevmode\hypertarget{ref-Iacona2017}{}%
Iacona, G. D., H. P. Possingham, and M. Bode. 2017. Waiting can be an
optimal conservation strategy, even in a crisis discipline. Proceedings
of the National Academy of Sciences 201702111.

@@

\leavevmode\hypertarget{ref-Marescot2013}{}%
Marescot, L., G. Chapron, I. Chadès, P. L. Fackler, C. Duchamp, E.
Marboutin, and O. Gimenez. 2013. Complex decisions made simple: a primer
on stochastic dynamic programming. (R. Freckleton, ed.)Methods in
Ecology and Evolution 4:872--884.

>>>>

\leavevmode\hypertarget{ref-sarsop-pkg}{}%
Boettiger, C., J. Ooms, and M. Memarzadeh. 2018. sarsop: Approximate
POMDP Planning Software in R, v0.5.0,
\textless{}https://github.com/boettiger-lab/sarsop\textgreater{}.

@@

\leavevmode\hypertarget{ref-Dorner2009}{}%
Dorner, B., R. M. Peterman, and Z. Su. 2009. Evaluation of performance
of alternative management models of Pacific salmon (Oncorhynchus spp.)
in the presence of climatic change and outcome uncertainty using Monte
Carlo simulations. Canadian Journal of Fisheries and Aquatic Sciences
66:2199--2221.

@@

\leavevmode\hypertarget{ref-Iacona2017}{}%
Iacona, G. D., H. P. Possingham, and M. Bode. 2017. Waiting can be an
optimal conservation strategy, even in a crisis discipline. Proceedings
of the National Academy of Sciences 114:201702111.

@@

\leavevmode\hypertarget{ref-Marescot2013}{}%
Marescot, L., G. Chapron, I. Chadès, P. L. Fackler, C. Duchamp, E.
Marboutin, and O. Gimenez. 2013. Complex decisions made simple: a primer
on stochastic dynamic programming. Methods in Ecology and Evolution
4:872--884.
